Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-21 2015-turklang-kazdep/paper.tex
updas
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60982 72bbbca6-d526-0410-a7d9-f06f51895060

One difference in our annotation scheme compared to the standard universal dependency
analysis is with coordination. While the universal dependency scheme takes the first
conjunct as the head, we take the last. This decision was made based on the fact that
Kazakh is a head-final language and morphological marking is only obligatory on the
last conjunct in a series. Furthermore, experiments in representing coordination
in other head-final languages have found that the final-conjunct head analysis 
results in better parser accuracy \parencite{bengoetxea09}.

@@

There are different ways in which two nominals may occur together to act as a single nominal.  Compounds are formed by an attributive nominal (indistinguishable from the bare / nominative form, but tagged with \tag{attr}) preceding another nominal, as shown in \ref{fig:compound}.  An indefinite genitive construction is formed by an indefinite genitive nominal (indistinguishable from the bare / nominative form, and tagged with \tag{nom}) preceding a nominal that has third-person possessive morphology, as shown in \ref{fig:indefgen}.  A definite genetive construction is formed by a genitive-marked nominal (tagged \tag{gen}) precding a nominal that has third-person possessive morphology, as shown in \ref{fig:defgen}.

>>>>

One difference in our annotation scheme compared to the standard universal dependency
analysis is with coordination. While the universal dependency scheme takes the first
conjunct as the head, we take the last. This decision was made based on the fact that
Kazakh is a head-final language and morphological marking is only obligatory on the
last conjunct in a series. Furthermore, experiments in representing coordination
in other predominantly head-final languages have found that the final-conjunct head analysis 
results in better parser accuracy \parencite{bengoetxea09}.

@@

There are different ways in which two nominals may occur together to act as a single nominal.  Compounds are formed by an attributive nominal (indistinguishable from the bare / nominative form, but tagged with \tag{attr}) preceding another nominal, as shown in \ref{fig:compound}.  An indefinite genitive construction is formed by an indefinite genitive nominal (indistinguishable from the bare / nominative form, and tagged with \tag{nom}) preceding a nominal that has third-person possessive morphology, as shown in \ref{fig:indefgen}.  A definite genitive construction is formed by a genitive-marked nominal (tagged \tag{gen}) precding a nominal that has third-person possessive morphology, as shown in \ref{fig:defgen}.
